A comprehensive framework to capture the arcana of neuroimaging analysis

### 2019-03-13 manuscript/manuscript.tex
reworked Pipeline.add paragraph to describe new structure

Interface traits are connected to inputs and outputs of the pipeline by
providing \emph{inputs} and \emph{outputs} keyword arguments to the \emph{add} method. Both
arguments take a dictionary, where the keys of the dictionary are the names of traits of the interface. The
values of the dictionary are 2-tuples each consisting of the name of a data specification
and the format the pipeline either expects or produces the data in (i.e. a FileFormat for Fileset specifications
or Python datatype for Field specifications). If the expected format does not match that of the
corresponding data specification or study input then a conversion node is implicitly connected
to the pipeline. Inputs and outputs that are conditional on parameters or inputs provided to the
study can be set outside of the \emph{add} method using the \emph{connect\_input} or
\emph{connect\_output} methods, respectively.

Connections between nodes are specified by a dictionary
passed to the \emph{connect} keyword argument of the \emph{add} method
that creates the receiving node. The dictionary keys are the names of the
receiving traits and the values are 2-tuples
consisting of the sending node and the name of the sending trait. Alternatively,
conditional connections can be specified via the \emph{connect} method of the
pipeline, which simply calls the method of the same name in the underlying
Nipype workflow.

>>>>

Node interfaces are connected to each other, and to inputs and outputs of the pipeline, by
providing \emph{inputs} and \emph{outputs} keyword arguments to the \emph{add} method. Both
arguments take a dictionary. The keys of the \emph{inputs} dictionary correspond to
trait names in the node's input interface, whereas the keys of the \emph{outputs} dictionary correspond to
names of entries in the data specification table. The values of both dictionaries are 2-tuples. For pipeline
inputs, values of the \emph{inputs} dictionary consist of a name of an entry in the data specification table
and the format the input is expected in (i.e. a FileFormat for Fileset specifications or Python datatype for Field specifications).
For pipeline outputs, values of the \emph{outputs} dictionary consist of a trait name in the node's output interface and the format the
output data is generated in. For input connections from other nodes, values of the \emph{inputs} dictionary
consist of a reference to the upstream node and the name of a trait in the
upstream node's output interface (output connections are implied by input connections to other nodes).

If the expected format of a pipeline input or generated format of a pipeline output does not match that
of the corresponding study input or data specification, then a conversion node is implicitly connected
to the pipeline by the framework to perform the required conversion. Pipeline inputs and outputs of
that are conditional on parameters or inputs provided to the study can be specified outside of the
\emph{add} method using the \emph{connect\_input} or
\emph{connect\_output} methods, respectively. Conditional connections between
nodes can be specified via the \emph{connect} method of the pipeline (which simply calls the
method of the same name in the underlying Nipype workflow).
